\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-04 manuscript.Rmd

#Commonality
Fac.5 <- fa.5F.3
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)

# loadings
min.loadings <- min(Fac.5$loadings)
max.loadings <- max(Fac.5$loadings)

@@

LB.model.Cor.1 <- "F1 =~ item16 + item36 + item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a1*item32 +item35 + Ritem37 + item38+ a2*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1+ item26

@@

## Selected Fit measures 
fit.1 <- fitmeasures (fit.Cor.1,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.scaled","tli.scaled",
                       "rmsea.robust", 
                       "srmr","aic"))

@@

## Selected Fit measures 
fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.scaled","tli.scaled",
                       "rmsea.scaled", 
                       "srmr","aic"))

>>>>

#Communality
Fac.5 <- fa.5F.3
min.com <- min(Fac.5$communality)
max.com <- max(Fac.5$communality)

# loading
min.loadings <- min(Fac.5$loadings)
max.loadings <- max(Fac.5$loadings)

@@

LB.model.Cor.1 <- "F1 =~ item16 + item36 + item17
                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                 F3 =~  item27+ item3+ item40 + item30 + item41
                 F4 =~ a1*item32 +item35 + Ritem37 + item38+ a2*item33 
                 F5 =~ item46+ item45+ item25+ item4+ item1+ Ritem26

@@

## Selected Fit measures 
fit.1 <- fitmeasures (fit.Cor.1,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.scaled","tli.scaled",
                       "rmsea.scaled", 
                       "srmr"))

@@

## Selected Fit measures 
fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.scaled","tli.scaled",
                       "rmsea.scaled", 
                       "srmr"))
